\chapter{Instructions for User Study}
\label{appendix:instructions}

\section{Opening}
Hi, thank you for coming to participate my experiment. The aim of my dissertation is to develop a system that can detect people’s posture and provide real time feedback. Your participation would be helpful for me to model some postures and find the general behavior pattern in some scenarios. Please read the information sheet and sign on the consent sheet. If you have any question, you are welcome to ask anytime.

\section{Section 1}
In the first section, we are going to measure some postures. Please relax and sit on the chair with my appointed posture. If you have any question about the appointed posture don’t hesitate to ask. You can do any activity you like such as using your smart phone or watching TV. First, please sit properly in your most comfortable and usual way.

(After three minutes) This is the first part of this section. Now I would like to ask you some question about this your experience on the posture and your answer should range between 1 to 5. 5 is very positive, and 1 is very negative:

\begin{enumerate}
  \item To what extend did you relax?
  \item How's the similarity between your posture in current condition and in your daily life?
  \item Please also feel your body. How’s the current comfort to your neck?
  \item How’s the current comfort to your shoulder?
  \item How’s the current comfort to your spine?
\end{enumerate}

(The procedure would be repeated for each posture according to the order of the assigned group for each participant)

\section{Section 2}
The second section is a scenario study. Your task is to sit on the sofa and use your own mobile device/ watch the TV. (If the participant asked anything about postures, answer ``just make yourself at home.'')

(After 15 minutes) Time's up. To what extend did you relax when you were doing the activity? How similar there is between your current posture and your usual posture in this scenario? 

\section{Section 3}
The section three is a brief interview.I would like to understand more about your posture pattern and the way that might help you to improve it.\\

\begin{enumerate}
  \item First, do you have any musculoskeletal disorder history? If any, do you mind to specify it?
  \item Do you have any musculoskeletal discomfort in the past three months and why do you think they come?
  \item To what extend do you think your posture is appropriate and healthy? 1-5
  \item How often are you aware that you are having bad postures? In what timing are you usually aware that you are having bad posture?
  \item What effort did you make to correct bad postures? (Method, duration, result)
  \item What can motivate you to have better postures?
  \item Can you distribute the 100 tokens to different benefits of having good postures according to their importance to you?
  \item Can you distribute the 100 tokens to different feedback methods according to the efficiency you believe it can have for you when you are at home?
  \item Can you distribute the 100 tokens using the same table according to the willingness for you to install such a system at home?
  \item Can you distribute the 100 tokens to different perceptual channels, which can be used to receive the feedback of posture at home, according to the efficiency you believe it can have for you?
  \item Can you distribute the 100 tokens to different perceptual channels, which can be used to receive the feedback of posture at home, according to your preference for receiving such kind of message in the form?
\end{enumerate}

\section{Wrapping up}
The experiment is finished.If you feel any physical uncomfortable,a consulting service is available by calling 111. If you are interested in the result of the research or the analysis of your personal data, please leave your email address and I am very happy to send you a copy of it after it is done. Thank you for your participation. Good bye!
