\chapter{Interview Instructions for Evaluation}
\label{appendix:interview_instructions}

This section is the final part of my study. I will read some statements, please reply me by choosing a number from one to five. Five is strongly agree, one is strongly disagree. If you have any question about the statement, or feel anything unclear, please don’t hesitate to ask.

\begin{enumerate}
  \item I thought the feedback is consistent in this system.
  \item I found the different functions of this system were well integrated.
  \item I thought the feedback provided by the system was easy to understand.
  \item I could understand the meaning of the feedback without much learning.
  \item I found the system could catch my posture sensitively.
  \item I found the system could categorise my posture correctly.
  \item I found the android app is easy to use.
  \item I found the settings of the android app could be easily modified.
  \item I was aware that my posture could be unhealthy when I saw a feedback of my bad posture.
  \item I tended to improve my posture when I received a feedback of the bad posture.
  \item I found the feedback of the system was unnecessarily complex.
  \item I like the design of the graphical feedback.
  \item I felt offended when I received a feedback for my bad posture.
  \item I felt positive when I improved the posture with the aid of the system.
  \item I felt positive when my good posture was captured by the system.
  \item If you had all necessary equipment, how often would you like to use the system? 1 is rare, 2 is seldom, 3 is sometimes, 4 is often, 5 is frequently.
\end{enumerate}

The other questions are open-ended; feel free to provide any opinion on the system.

\begin{enumerate}
  \item What did you feel when you received the angel/devil feedback?
  \item What do you think about the design of the angel/ devil feedback?
  \item What did you feel when you received the individual head tracking feedback?
  \item What do you think about the design of the individual head tracking feedback?
  \item What do you think if you replace the cartoon style skeleton with the real skeleton of the user?
  \item What did you feel when you received the feedback from the mobile device?
  \item What do you think about the design of the mobile app?
\end{enumerate}
